\chapter{Reflections}

\paragraph{}
Throughout my senior project, I learned a lot about how to manage my time, how to properly set requirements, and how to design a system that interacts with pre-existing systems and goals.
For my, the largest challenge I faced as an engineer was my time management skills.
It was difficult attempting to balance getting this project finished on time while balancing the rest of my courses and holding a leadership role in a time-demanding club.
Something that helped me was finding gaps of time where I could treat working on senior project as a more structured class, having 1 or 2 hour periods of time where this was the only task I was working on several times per week.

\paragraph{}
Something else I learned was how to change scopes or change ideas when things are not working.
This finished project was not the same topic as when I first started senior project.
Originally, I was working on integrating hardware accelerators with the Zybo-Z7 processor.
Specifically, I was looking into adding a FFT hardware accelerator for processing an audio input.
I struggled to work on this project due to a host of issues with poor documentation on resources for the development board, a change of academic interests away from FPGA design, and growing interests in embedded systems and signal processing projects instead.
As a result, the scope of this project changed into more pure embedded systems project that had a more attainable scope for an individual senior project.
As unfortunate as it was to not be able to follow through on the original design plans for my senior project, it helped me grow as an engineer.

\paragraph{}
Finally, I was able to become a better communicator while working on this project.
Even though the senior project itself was individual, it was for a club project and as a result, there was a significant amount of communication occurring between myself and other members of the club to make sure that features that were wanted could be added so that everyone's needs were being met.
Communication was also critical due to this project needing to be integrated into an existing electronics system.
Without strong communication, integration issues could have become a major problem.