\section{MoTeC}

\paragraph{}
A third company that makes data logging solutions for automotive application is MoTeC\cite{MoTeCSite}.
MoTeC is an automotive aftermarket company owned by Bosch that focuses on making electronic equipment for race sport uses.
They make ECUs, data loggers, dashboards, PDMs, and several other products that can be used to monitor or improve the performance of vehicles.
These products are similar in spec to the products made by AEM and AiM.

\subsection{MoTeC Loggers}

\paragraph{}
Similarly to AEM and AiM, MoTeC offers both independent logger units as well as combined dash and logger units.
These loggers have similar specs to the AEM and AiM loggers, with the basic functionality of CAN channels, RS-232 channels, analog sensor inputs, digital sensor inputs, and the ability to use expansion units to increase the total amount of available connectivity.
The dashboard options are very similar to the dashboards available from AEM and AiM.

\paragraph{}
There are three available options that support the full range of connectivity for a combined dash and logger and three additional options for just the logger.
The cheapest of the dash and logger combined units, the C125, costs approximately \$2,200 from third part retailers before any additional add-ons are acquired.
The cost of the cheapest logging only option, the L120, costs approximately \$1,800 from third party retailers.
These prices are higher than the previously discussed AiM and AEM options.

\paragraph{}
One of the main differences between this option when compared to the AEM or AiM loggers is that none of the available loggers or combined dash and loggers have telemetry available.
In order to add telemetry data, an additional fee or upgrade is required to add the MoTeC T2 Telemetry features.

\subsection{MoTeC Add-Ons}

\paragraph{}
Like the AEM and AiM, MoTeC also makes different devices and sensors to compliment their data loggers to improve the overall functionality and compatibility.
MoTeC makes an expander unit, similar to the CAN expander made by AiM called the SVIM that can collect several different analog or digital sensors and connect to the CAN network for the MoTeC.
Additionally, MoTeC makes an expansion unit called the E888 that has similar features the the SVIM, but includes thermocouple specific inputs.
This unit additionally is more limited on which loggers it can connect to, only being compatible with the SDL3 logger and the ACL logger.

\paragraph{}
In addition to the expansion units, MoTeC also makes various sensors that can be connected to the loggers or expansion units.
Similarly to AEM and AiM, they make thermocouples, various temperature sensors, pressure sensors, and speed sensors.
Additionally, they also make linear and rotary potentiometers for applications such as steering angle measurements or suspension travel measurements as well as an IMU.
Just like AiM, these sensors are not sold directly by MoTeC and must instead purchased from a third party retailer.
These sensors are somewhat expensive but comparable in price to the sensors made by AEM and AiM.